\hspace{1cm} Do syntactic and semantic similarity lead to interference effects?\newline Evidence from self-paced reading and event-related potentials using German

### 2023-10-14 paper/main.tex
Update main.tex
discussion of modeling edited

\begin{table}[]
    \caption{Relatively informative priors for the analysis of the event-related potentials \citep{nicenboim_stats}. Priors on the slope parameters were truncated to an upper bound of zero, i.e., only negative values. This corresponds to more negative brain responses to high vs.\ low interference conditions in line with the literature. The standard deviations of the slope priors were varied in order to conduct a Bayes factor sensitivity analysis. See the corresponding assumed a priori range of the difference between high vs.\ low interference.}
    \label{tab:eeg_priors}
    \centering
    \begin{tabular}{lllr}
    \toprule
    Parameter&Prior & &Assumed Range ($\mu V$)\\
    \midrule
  Intercept & Normal(2, 5)& &\\
  \cmidrule{2-4}
  \multirow{4}{1cm}{beta} & Normal(0, 0.1) &\hspace{-1em}\rdelim\}{3}{*}[upper bound: 0]& [-0.2, - 0]\\
  &  Normal(0, 0.5)& & [-1, 0]\\
  & Normal(0, 1) && [-2, 0]\\
  & Normal(0, 5) && [-11, 0]\\
  \cmidrule{2-4}
  sigma & Normal(10, 5)& \hspace{-1em}\rdelim\}{2}{*}[lower bound: 0]\\
  SD & Normal(0, 2)&\\
    \bottomrule
    \end{tabular}
\end{table}

@@

Consistent with the self-paced reading study, there is clear evidence for semantic interference, and evidence against syntactic interference.  How do these observed patterns compare to the theoretical predictions of cue-based retrieval theory? It turns out that the answer to this question crucially depends on which cues one assumes are being used during retrieval. We turn to this point next by discussing the predictions of the \cite{Lewis2005} model.

@@

\section{Quantitative predictions of the Lewis and Vasishth (2005) model for the current design}
% stopped here xxx

>>>>

\begin{table}[]
    \caption{Relatively informative priors for the analysis of the event-related potentials \citep{nicenboim_stats}. Priors on the slope parameters were truncated to an upper bound of zero, i.e., only negative values. This corresponds to more negative brain responses to high vs.\ low interference conditions in line with the literature. The standard deviations of the slope priors were varied in order to conduct a Bayes factor sensitivity analysis. See the corresponding assumed a priori range of the difference between high vs.\ low interference.}
    \label{tab:eeg_priors}
    \centering
    \begin{tabular}{lllr}
    \toprule
    Parameter&Prior & &Assumed Range ($\mu V$)\\
    \midrule
  Intercept & Normal(2, 5)& &\\
  \cmidrule{2-4}
  \multirow{4}{1cm}{slope} & Normal(0, 0.1) &\hspace{-1em}\rdelim\}{3}{*}[upper bound: 0]& [-0.2, - 0]\\
  &  Normal(0, 0.5)& & [-1, 0]\\
  & Normal(0, 1) && [-2, 0]\\
  & Normal(0, 5) && [-11, 0]\\
  \cmidrule{2-4}
  sigma & Normal(10, 5)& \hspace{-1em}\rdelim\}{2}{*}[lower bound: 0]\\
  SD & Normal(0, 2)&\\
    \bottomrule
    \end{tabular}
\end{table}

@@

Consistent with the self-paced reading study, there is clear evidence for semantic interference, and evidence against syntactic interference.  How do these observed patterns compare to the theoretical predictions of cue-based retrieval theory? We turn to this point next by discussing the quantiative predictions of the \cite{Lewis2005} model.

@@

\section{Quantitative predictions of the Lewis and Vasishth (2005) model for the present design}

 \cite{mertzen} presented simulations that show approximately equally sized interference effects 
for both the syntactic and semantic manipulations. Figure \ref{fig:model_predictions} reproduces thes simulations; these are prior predictive distributions of the effects of interest, holding all parameters in the model at fixed values and sampling from a prior distribution ($Beta(a=4,b=6)$), for the scaling parameter F in the \citet{Lewis2005}. This parameter scales the activation to a retrieval time.

The \citet{Lewis2005} model does not only overestimate the effect size of semantic interference, but it also predicts equally sized semantic and syntactic interference effects (see Figure \ref{fig:model_predictions}).
